$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-07-23 paper/paper.tex
Clarify the variable typing example

  We lift the operation $\op{x}{y}{z}$ and its algebraic properties to an operation $\opsquared{x_l \comma x_r}{y_l \comma y_r}{z_l \comma z_r}$ on pairs of multiplicities and an operation $\opctx{\Gamma}{\Delta}{\Xi}$ on usage contexts with the same underlying context of indices.

@@

\begin{example}[Variable reference]
  Let us illustrate the use of variable reference relations with an example in \autoref{lst:channels}.
  \begin{lstlisting}[label=lst:channels,mathescape,numbers=left,caption=Typing variable reference $\suc \constr{0}$ with type $\channel{\unit}{\li}$ and usage $\li$.]
  _ : $\contains{\constr{[]} \comma \channel{\unit}{\li} \comma \unit} {\constr{[]} \comma \lio \comma \lio} {\suc \; \constr{0}} {\channel{\unit}{\li}} {\li} {\constr{[]} \comma \lo \comma \lio}$
  _ = $\suc \; \constr{0}$
  \end{lstlisting}
  The underscore \_ introduces an anonymous declaration immediately followed by its definition.
  The constructor $\suc$ steps under the outermost variable in the context, preserving its usage annotation $\lio$ from input to output.
  The constructor $\constr{0}$ asserts that the next variable is of a channel type $\channel{\unit}{\li}$, and that we can split its input annotation $\lio$, taking away $\li$ and leaving $\lo$ as the leftover, to be used later on.
\end{example}

>>>>

  We lift the operation $\op{x}{y}{z}$ and its algebraic properties to an operation $\opsquared{(x_l \comma x_r)}{(y_l \comma y_r)}{(z_l \comma z_r)}$ on pairs of multiplicities and an operation $\opctx{\Gamma}{\Delta}{\Xi}$ on usage contexts with the same underlying context of indices.

@@

\begin{example}[Variable reference]
  \autoref{lst:channels} types a variable reference under a linear algebra.
  \begin{lstlisting}[label=lst:channels,mathescape,numbers=left,caption=Typing variable reference $\suc \constr{0}$ with type $\channel{\unit}{\li}$ and usage $\li$.]
  _ : $\contains{\constr{[]} \comma \channel{\unit}{\li} \comma \unit} {\constr{[]} \comma \lio \comma \lio} {\suc \constr{0}} {\channel{\unit}{\li}} {\li} {\constr{[]} \comma \lo \comma \lio}$
  _ = $\suc \constr{0}$
  \end{lstlisting}
  The underscore \_ introduces an anonymous declaration immediately followed by its definition.
  We must show that the variable at position $\suc \constr{0}$ is of type $\channel{\unit}{\li}$ and has a usage annotation $\li$ in an environment with a typing context $\constr{[]} \comma \channel{\unit}{\li} \comma \unit$ and a usage context $\constr{[]} \comma \lio \comma \lio$.
  Which \textsc{VarRef} constructors to use is completely determined by the $\suc \; \constr{0}$ in the type.
  The constructor $\suc$ steps under the outermost variable in the context, preserving its usage annotation $\lio$ from input to output.
  The constructor $\constr{0}$ asserts that the next variable is of type $\channel{\unit}{\li}$, and that we can split its input annotation $\lio$, taking away $\li$ and leaving $\lo$ as the leftover.
\end{example}
